---
title: "Module_2"
author: "Duohan Zhang"
date: "10/12/2022"
output: html_document
---

```{r}
dat = read.csv("BodyFat.csv")
#delete the abnormal data
dat = dat[-c(42,172,182),]
model1 = lm(BODYFAT ~ DENSITY, data = dat)
model2 = lm(BODYFAT ~ AGE, data = dat)
model3 = lm(BODYFAT ~ WEIGHT, data = dat)
model4 = lm(BODYFAT ~ HEIGHT, data = dat)
model5 = lm(BODYFAT ~ ADIPOSITY, data = dat)
model6 = lm(BODYFAT ~ NECK, data = dat)
model7 = lm(BODYFAT ~ CHEST, data = dat)
model8 = lm(BODYFAT ~ ABDOMEN, data = dat)
model9 = lm(BODYFAT ~ HIP, data = dat)
model10 = lm(BODYFAT ~ THIGH, data = dat)
model11 = lm(BODYFAT ~ KNEE, data = dat)
model12 = lm(BODYFAT ~ ANKLE, data = dat)
model13 = lm(BODYFAT ~ BICEPS, data = dat)
model14 = lm(BODYFAT ~ FOREARM, data = dat)
model15 = lm(BODYFAT ~ WRIST, data = dat)
```

```{r}
rmse = numeric(15)
rmse[1] = sqrt(mean((model1$residuals)^2))
rmse[2] = sqrt(mean((model2$residuals)^2))
rmse[3] = sqrt(mean((model3$residuals)^2))
rmse[4] = sqrt(mean((model4$residuals)^2))
rmse[5] = sqrt(mean((model5$residuals)^2))
rmse[6] = sqrt(mean((model6$residuals)^2))
rmse[7] = sqrt(mean((model7$residuals)^2))
rmse[8] = sqrt(mean((model8$residuals)^2))
rmse[9] = sqrt(mean((model9$residuals)^2))
rmse[10] = sqrt(mean((model10$residuals)^2))
rmse[11] = sqrt(mean((model11$residuals)^2))
rmse[12] = sqrt(mean((model12$residuals)^2))
rmse[13] = sqrt(mean((model13$residuals)^2))
rmse[14] = sqrt(mean((model14$residuals)^2))
rmse[15] = sqrt(mean((model15$residuals)^2))
rmse
```

From the above results we see that the 8th model is the best one in the sense that it has the lowest Root Mean Square Error.


```{r}
library(ggplot2)
model = lm(BODYFAT ~ ABDOMEN, data = dat)
ggplot(dat, aes(ABDOMEN, BODYFAT)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "red")
coef = model$coefficients
```

Outlier detection
delete 39th data point
```{r}
clean_dat = dat[-c(39),]
new_model = lm(BODYFAT ~ ABDOMEN, data = clean_dat)
summary(new_model)
ggplot(clean_dat, aes(ABDOMEN, BODYFAT)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "red")
coef = new_model$coefficients
```

Test whether the density is significant
```{r}
summary(new_model)
# calculate standardized residuals
standard_res = rstandard(new_model)
```

model diagnostics
1. check normaility
```{r}
qqnorm(standard_res, pch = 20)
qqline(standard_res, col = "red")
```

# Checking equality of variance
```{r}
ggplot() +
  geom_point(aes(new_model$fitted.values, new_model$residuals)) +
  xlab("Fitted Values") + 
  ylab("Residuals")

```

```{r}
plot(new_model)
```

Delete 180th, 204th, 207th data point,since their residues are too large.

```{r}
final_dat = clean_dat[-c(207,204,180),]
new_model2 = lm(BODYFAT ~ ABDOMEN, data = final_dat)
ggplot(final_dat, aes(ABDOMEN, BODYFAT)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, col = "red")

coef = new_model2$coefficients
```

```{r}
summary(new_model2)
standard_res = rstandard(new_model2)
```

model diagnostics

1. check normaility
```{r}
qqnorm(standard_res, pch = 20)
qqline(standard_res, col = "red")
```

# Checking equality of variance
```{r}
ggplot() +
  geom_point(aes(new_model2$fitted.values, new_model2$residuals)) +
  xlab("Fitted Values") + 
  ylab("Residuals")

```

```{r}
plot(new_model2)
```
